\documentclass[letterpaper]{article}

\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[margin=1in]{geometry}

\begin{document}

% Title -----------------------------------------------------------------------

\title{Reading 04: Diversity At Notre Dame}
\date{}
% TODO: EDIT
\author{Domer McDomerson {\textless}dmcdomer@nd.edu{\textgreater}}

\maketitle

% Overview --------------------------------------------------------------------

\section*{Overview}

\paragraph{}

% TODO: REMOVE and EDIT
This provides a {\bf brief} overview (a paragraph) of what you did, how you did
it, what you discovered, and what your main takeaway was.

% Methodology -----------------------------------------------------------------

\section*{Methodology}

\paragraph{}

% TODO: REMOVE and EDIT
This briefly describes how you processed the {\tt demographics.csv} data and
how you produced the graphs. In particular, it should discuss any interesting
or frustrating problems you faced and how you overcame them. You may include
\href{https://en.wikibooks.org/wiki/LaTeX/Source_Code_Listings}{code listings}
of your shell scripts if you wish (as long as you provide some description to
accompany the code).

% Analysis --------------------------------------------------------------------

\section*{Analysis}

% TODO: INSERT TABLE

\paragraph{}

% TODO: REMOVE and EDIT
This should provide tables that summarize the {\tt demographics.csv} data and
graphs that provide insight into the questions:

% TODO: INSERT FIGURE

\begin{enumerate}

\item{}What is the overall trend in gender balance in the Computer Science and
    Engineering program at the University of Notre Dame?

\item{}How has ethnic diversity changed over time in the Computer Science and
    Engineering program at the University of Notre Dame?

\end{enumerate}

% TODO: INSERT FIGURE

You should accompany these tables and graphs with some commentary on the
meaning of the data and plots.

\paragraph{}

% Discussion ------------------------------------------------------------------

\section*{Discussion}

\paragraph{}

% TODO: REMOVE and EDIT
This final section is an opportunity for you to reflect on the issue of
creating a {\bf welcoming} and {\bf supportive} learning environment at the
University of Notre Dame. For instance, you may wish to discuss any of the
following questions:

\begin{enumerate}

\item{}Are the issues of gender and ethnic diversity important to you? Should
    the department work to increase diversity? Should the technology industry
    	try to improve workplace diversity? Why or why not?

\item{}Does the Computer Science and Engineering department provide a welcoming
    and supportive learning environment to all students? In what ways can it
    	improve?

\item{}What challenges have you experienced thus far in the Computer Science
    and Engineering program? How could the department or university better
    	support you?

\end{enumerate}

\end{document}
